---
title: "Homework2"
author: "Cüneyt Çakır"
date: "07 05  2021"
output: 
  html_document:
      fig_width: 9
      fig_height: 6
      fig_caption: true
      code_folding: hide
      toc: true
      toc_float: true
      toc_depth: 4 
      number_sections: true
      theme: united
      highlight: pygments 
      
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Package Installing 

I install some packages before i start out analysis.

```{r warning=FALSE, message=FALSE}
library(readxl)
library(ggplot2)
library(dplyr)
library(tidyr)
library(lubridate)
library(RColorBrewer)
library(zoo)
library(data.table)
library(plotly)
```
# Data Information

I take four datasets from [EVDS](https://evds2.tcmb.gov.tr/). These are:
  "-House Sales Statistics - Turkey-House Sales Statistics - Mortgaged sales",
  "-Housing (TRY)-Weighted Average Interest Rates For Banks Loans",
  "-Financial situation of household expectation - Seasonally unadjusted Consumer Confidence Index and Indices of Consumer Tendency Survey Questions", 
  "-Dollar Exchange Rate"
```{r warning=FALSE, message=FALSE, echo=FALSE}
dollar_buying<-read_excel("C:/Users/froze/OneDrive/Masaüstü/3600/dollar_buying.xlsx")
house_sales<-read_excel("C:/Users/froze/OneDrive/Masaüstü/3600/house_sales.xlsx")
housing_interest<-read_excel("C:/Users/froze/OneDrive/Masaüstü/3600/housing_interest.xlsx")
household<-read_excel("C:/Users/froze/OneDrive/Masaüstü/3600/household.xlsx")
```
After receiving the data, i manipulated the data.    

```{r warning=FALSE, message=FALSE, echo=FALSE}

house_sales_new <- setDT(house_sales)
sum(is.na(house_sales_new))
sum(duplicated(house_sales_new))
house_sales_new <-house_sales_new%>%rename(Date=Date,Expenditure=`TP AKONUTSAT2 TOPLAM`)%>%
  mutate(Date=as.Date(as.yearmon(Date)))
house_sales_new %>% glimpse()

dollar_buying_new<-setDT(dollar_buying)
sum(is.na(dollar_buying_new))
sum(duplicated(dollar_buying_new))
dollar_buying_new <-dollar_buying_new%>%rename(Date=Date,Rate=`TP DK USD A YTL`)%>%
   mutate(Date=as.Date(as.yearmon(Date)))
dollar_buying_new %>% glimpse()

housing_interest_new<-setDT(housing_interest)
sum(is.na(housing_interest_new))
sum(duplicated(housing_interest_new))
housing_interest_new <-housing_interest_new%>%rename(Date=Date,Interest=`TP KTF12`)%>%
   mutate(Date=as.Date(as.yearmon(Date)))
housing_interest_new %>% glimpse()

household_new<-setDT(household)
sum(is.na(household_new))
sum(duplicated(household_new))
household_new <-household_new%>%rename(Date=Date,Expectation=`TP TG2 Y03`,Real=`TP TG2 Y02`)%>%
  mutate(Date=as.Date(as.yearmon(Date)))
household_new %>% glimpse()

```
# Visualiton of Datasets


```{r warning=FALSE, message=FALSE}
ggplotly(
ggplot(data=house_sales_new, aes(x=Date, y=Expenditure)) +
  geom_line(color="red")+
  geom_point()+theme(plot.title = element_text(hjust = 0.5))+
  labs(
    title = "House Sales Statistics - Turkey - Mortgaged sales",
    x = "Date",
    y = "Expenditure"
  ))
```


```{r warning=FALSE, message=FALSE}
ggplotly(
ggplot(data=dollar_buying_new, aes(x=Date, y=Rate, group=1)) +
  geom_line(color="red")+
  geom_point()+theme(plot.title = element_text(hjust = 0.5))+
  labs(
    title = "Dollar Exchange Rate",
    x = "Date",
    y = "Rate"
  ))
```


```{r warning=FALSE, message=FALSE}

ggplot(data=household_new, aes(x=Date, y=Expectation, group=1))+
  geom_line(color="red")+
  geom_point()+theme(plot.title = element_text(hjust = 0.5))+
  labs(
    title = "Financial Situation of Household Expectation - Survey",
    x = "Date",
    y = "Interest"
)

ggplot(data=household_new, aes(x=Date, y=Real, group=1))+
  geom_line(color="red")+
  geom_point()+theme(plot.title = element_text(hjust = 0.5))+
  labs(
    title = "Financial Situation of Household-Survey",
    x = "Date",
    y = "Real"
)

```


```{r warning=FALSE, message=FALSE}
ggplotly(
ggplot(data=housing_interest_new, aes(x=Date, y=Interest, group=1)) +
  geom_line(color="red")+
  geom_point()+theme(plot.title = element_text(hjust = 0.5))+
  labs(
    title = "I.R for Bank Loans",
    x = "Date",
    y = "Interest"
  ))
```

# Modelling



```{r warning=FALSE, message=FALSE}
# sort each with date

house_sales_new<-house_sales_new[order(Date),]
household_new<-household_new[order(Date),]
housing_interest_new<-housing_interest_new[order(Date),]
dollar_buying_new<-dollar_buying_new[order(Date),]
```

```{r warning=FALSE, message=FALSE}
# sort each with date

lag.count<-6
take.year.lag<-function(array_){
  df<-c()
  for (i in 1:lag.count){
    df<-cbind(df,lag(array_,n=i))
  }
  return(df)
}


house_sales_new_lags=take.year.lag(house_sales_new$Expenditure)
lag_col_names=c()
for (i in 1:lag.count){
  lag_col_names=append(lag_col_names,paste0("Expenditure_lag_",i))
}
colnames(house_sales_new_lags)=lag_col_names

household_new_lags.Real=take.year.lag(household_new$Real)
lag_col_names=c()
for (i in 1:lag.count){
  lag_col_names=append(lag_col_names,paste0("Real_lag_",i))
}
colnames(household_new_lags.Real)=lag_col_names

household_new_lags.Expectation=take.year.lag(household_new$Expectation)
lag_col_names=c()
for (i in 1:lag.count){
  lag_col_names=append(lag_col_names,paste0("Expectation_lag_",i))
}
colnames(household_new_lags.Expectation)=lag_col_names

housing_interest_new_lags=take.year.lag(housing_interest_new$Interest)
lag_col_names=c()
for (i in 1:lag.count){
  lag_col_names=append(lag_col_names,paste0("Interest_lag_",i))
}
colnames(housing_interest_new_lags)=lag_col_names

dollar_buying_new_lags=take.year.lag(dollar_buying_new$Rate)
lag_col_names=c()
for (i in 1:lag.count){
  lag_col_names=append(lag_col_names,paste0("Rate_lag_",i))
}
colnames(dollar_buying_new_lags)=lag_col_names

```

```{r warning=FALSE, message=FALSE}

house_sales_main<-cbind(house_sales_new,house_sales_new_lags,household_new_lags.Real,household_new_lags.Expectation,housing_interest_new_lags,dollar_buying_new_lags)
house_sales_main<-na.omit(house_sales_main)

house_sales_main$Year<-as.numeric(format(house_sales_main$Date, format="%Y"))
house_sales_main$Month<-as.numeric(format(house_sales_main$Date, format="%m"))

model<-lm(Expenditure~.-Date,data=house_sales_main)
summary(model)

final.model<-step(lm(Expenditure~.-Date , data=house_sales_main),direction="backward")
summary(final.model)
```


```{r warning=FALSE, message=FALSE}
#model
#final.model
pred_df=c(21815,14669,10732,14631,24450,25566,67.16521,64.69312,62.11510,64.90300,65.9866,67.83600,87.92016,84.51865,83.80907,78.85528,79.02186,79.50939,17.7350,17.9850,18.3880,18.1925,15.6750,15.0660,7.628235,7.072365,7.393975,7.721065,8.003324,7.873881,2021,4)
pred_df=transpose(data.frame(pred_df))
colnames(pred_df)=colnames(house_sales_main)[3:length(colnames(house_sales_main))]

```
