---
title: "Interesting Forecasting Applications with R"
author: Cüneyt Çakır - IE360 - Spring 2021
---
```{r,echo=FALSE,results="hide"}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```

```{r,echo=FALSE,eval=FALSE}
rmarkdown::render("/home/baydogan/Courses/IE360/Guidelines/example_homework_0.Rmd",output_format="pdf_document")
rmarkdown::render("/home/baydogan/Courses/IE360/Guidelines/example_homework_0.Rmd",output_format="html_document")
```

1. [Time Series Forecasting Using R](https://www.pluralsight.com/guides/time-series-forecasting-using-r)

    In this guide, you will learn how to implement the following time series forecasting techniques using the statistical programming language 'R': 1. Naive Method 2. Simple Exponential Smoothing 3. Holt's Trend Method 4. ARIMA 5. TBATS

2. [Time Series Forecasting in R](https://towardsdatascience.com/a-guide-to-forecasting-in-r-6b0c9638c261)

    Here is what we will see in this article:
    Naive methods
    Exponential Smoothing (State-space models and DSHW)
    BATS and TBATS
    ARIMA/SARIMA models
    How to set up a one-step-ahead forecast
    
3. [The Best Guide to Time Series Forecasting in R](https://www.simplilearn.com/tutorials/data-science-tutorial/time-series-forecasting-in-r)

    Following are the topics that will be discussed in this article:
    What is Time Series Forecasting?
    Time Series Forecasting Applications
    Time Series Components
    Time Series Methods
    Time Series Forecasting Using The ARIMA Model
   
4. [Using R for Time Series Analysis](https://a-little-book-of-r-for-time-series.readthedocs.io/en/latest/src/timeseries.html)

    This booklet itells you how to use the R statistical software to carry out some simple analyses that are common in analysing time series data.
    
5. [Time Series Forecasting](http://r-statistics.co/Time-Series-Forecasting-With-R.html)

    This is a follow-up to the introduction to time series analysis, but focused more on forecasting rather than analysis.